\myChapter{Acknowledgements}
\label{chap:Acknowledgements}

The completion of this thesis marks the end of my Master's degree in Computer Science and represents a significant milestone in my life journey. I would like to take this opportunity to express my deepest gratitude to everyone who has supported and impacted me along the way. I apologize in advance to anyone I may inadvertently forget.

I would like to thank Professors Leonardo Grilli, Carla Rampichini, Emanuela Dreassi, Anna Gottard, Fabrizio Cipollini, Donatella Merlini, and Cecilia Verri from DISIA, as well as Professors Fabio Shoen, Marco Bertini, and Paolo Frasconi from DINFO. They not only taught me "maths stuff" but also contributed to my personal growth and development in various ways.

I am particularly grateful to my supervisor Marco Bertini and co-supervisor Leonardo Galteri for their invaluable guidance and the engaging conversations we shared during our weekly catch-ups while working on this thesis.

I would also like to thank Edoardo Baroncelli for making me believe I could succeed in Maths, and Sara, my psychotherapist, who helped me cope with my demons.

I appreciate the guidance and support of Marco Carrettoni and Luigi Di Lillo during my time as a Data Scientist at Swiss Re, and the people at Henesis who became not only coworkers but also friends: Riccardo Fava, Luca Baldini, Manuel Carzaniga, Davide Vurro, and Konstantin Koshmak. Special thanks to Luca Ascari, Maria Josè Vallejo, Freddy Symons, Stefano Lai, and Andrea Valenti for their direct and indirect help with my thesis.

Michele De Vita and Emilio Cecchini provided invaluable assistance during the initial stages of my Master's degree and became two of my closest friends.

Throughout my journey, I have been incredibly fortunate to meet individuals who have come to feel like family, touching my life with their warmth and support. With heartfelt affection, I extend my deepest gratitude to Matteo Lo Nigro, Simone Bonfanti, and Bruno Naselli from my early years in Quarrata; Giovanni Poli, Mirko Galardi, Tommaso Lenzi, Lorenzo Focardi, Shadi Moini, Noemi Benci, and Agnese Parca (aka "The Paranormals") who accompanied me through my undergraduate years; Emma Fani, Sole Urciullo, and Gabriele Montrone, who made my time spent at The Student Hotel truly memorable; and Marta Biondi and Lisa Modena (aka "GinJandPatate"), my current roommates in Parma who continue to brighten my days.

I would like to thank my family, including my father Massimo Palloni, with whom I had a complex and impactful relationship; my siblings Alessandro, Silvia, and Martina Palloni; my grandmother Gabriella Becagli; my uncles Gabriele and Gionata Finocchi; and my aunts Elena Finocchi and Ilaria Ciottoli. My mother, Beatrice Finocchi, has been my most significant support, and I am eternally grateful for her love and assistance.

Lastly, I want to thank Giovanni Barbarani, the most brilliant person I know and the closest person to me. Your influence on my life choices is immeasurable.

